# The Gapminder website contains over 500 data sets with information about
# the world's population. Your task is to continue the investigation you did at the
# end of Problem Set 3 or you can start fresh and choose a different
# data set from Gapminder.

# If you’re feeling adventurous or want to try some data munging see if you can
# find a data set or scrape one from the web.

# In your investigation, examine pairs of variable and create 2-5 plots that make
# use of the techniques from Lesson 4.

# You can find a link to the Gapminder website in the Instructor Notes.

# Once you've completed your investigation, create a post in the discussions that includes:
#       1. the variable(s) you investigated, your observations, and any summary statistics
#       2. snippets of code that created the plots
#       3. links to the images of your plots

# Copy and paste all of the code that you used for
# your investigation, and submit it when you are ready.


loading Quandl Piketty dataset.

```{r}
library(ggplot2)
setwd("/Users/guylalonde/Desktop/EDA/piketty_dataset")
ts9_3 <- read.csv("PIKETTY-TS9_3.csv", sep = ',')
names(ts9_3)
head(ts9_3)
ts9_3$date <- as.Date(ts9_3$Yaer)
ts9_3$year <- format(ts9_3$date, "%Y")
head(ts9_3)
min(ts9_3$year)
```


gathering and dropping columns

```{r}
library(tidyr)
gathered_ts9_3 <- gather(ts9_3, country, percent_income, 2:15, na.rm = TRUE)
head(ts9_3)
head(gathered_ts9_3)
keeps <- c('year', 'country', 'percent_income')
gathered_trimmed_ts9_3 <- gathered_ts9_3[keeps]
head(gathered_trimmed_ts9_3)
```

```{r}
?separate
vars <- c("Country", "percentile")
separate(data =ts9_3_B, col = country, into = vars, sep = regexpr(pattern ='\\W', 'hello..world'))
separate(data =ts9_3_B, col = country, into = vars, sep = '\\W')
head(ts9_3_B)
```

```{r}
library(stringr)
gathered_trimmed_ts9_3$split <- str_match(gathered_trimmed_ts9_3$country, "^(.*)[.][.](.*)$") [,-1]
head(gathered_trimmed_ts9_3)
gathered_trimmed_ts9_3
```

